---
title: "Stat 123 Assignment 3"
author: "Eric Huber"
date: "14/03/2022"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, prep}
HmwData = read.csv("homework3Data.csv")
```

## Question 1:


### (1.a)
```{r, q1a}

hist(HmwData$A, xlab = "x", main = "Histogram for Variable A", prob = TRUE)
abline(v =mean(HmwData$A), col="red")
abline(v = median(HmwData$A), col = "blue")
lines(density(HmwData$A), col = "green")

hist(HmwData$B, xlab = "x", main = "Histogram for Variable B", prob = TRUE)
abline(v =mean(HmwData$B), col="red")
abline(v = median(HmwData$B), col = "blue")
lines(density(HmwData$B), col = "green")

hist(HmwData$C, xlab = "x", main = "Histogram for Variable C", prob = TRUE)
abline(v =mean(HmwData$C), col="red")
abline(v = median(HmwData$C), col = "blue")
lines(density(HmwData$C), col = "green")

hist(HmwData$X, xlab = "x", main = "Histogram for Variable X", prob = TRUE)
abline(v =mean(HmwData$X), col="red")
abline(v = median(HmwData$X), col = "blue")
lines(density(HmwData$X), col = "green")

hist(HmwData$Y, xlab = "x", main = "Histogram for Variable Y", prob = TRUE)
abline(v =mean(HmwData$Y), col="red")
abline(v = median(HmwData$Y), col = "blue")
lines(density(HmwData$Y), col = "green")

hist(HmwData$Z, xlab = "x", main = "Histogram for Variable Z", prob = TRUE)
abline(v =mean(HmwData$Z), col="red")
abline(v = median(HmwData$Z), col = "blue")
lines(density(HmwData$Z), col = "green")
```


### (1.b)
The variable C appears to be normally distributed. We can see that our histogram is symmetric and our mean and median have the same value. The mean and median is also located in the center of our density curve which is bell shaped.


### (1.c)
```{r, q1c}
std = sd(HmwData$C)

sixtyeight = c((mean(HmwData$C)-std), (mean(HmwData$C)+std))
sixtyeight

ninetyfive = c((mean(HmwData$C)-(2*std)), (mean(HmwData$C)+(2*std)))
ninetyfive

ninetynine = c((mean(HmwData$C)-(3*std)), (mean(HmwData$C)+(3*std)))
ninetynine


```
Approximately 68% of the data falls between ~109.30-169.94, 95% of the data falls between ~78.91-200.27 and 99.7% falls between ~48.660-230.59.


### (1.d)
```{r, q1d}
quantile(HmwData$C, c(.16,.84))
quantile(HmwData$C, c(0.025, 0.975))
quantile(HmwData$C, c(0.0015, 0.9985))
```
We can see that the intervals are close, but definitely not the exact same. The first two (68% & 95%) are very close but the last one (99.7%) is a little further apart



### (1.e)
```{r, q1e}
xbar = mean(HmwData$C)
qnorm(c(0.16, 0.84), xbar, std )
qnorm(c(0.025, 0.975), xbar, std )
qnorm(c(0.0015, 0.9985), xbar, std )
```
We can see that the use of the qnorm() function gives us very similar output to the method used in part c and relatively similar to the method used in part d.


### (1.f)
```{r, q1f}
mean(HmwData$C)

n = length(HmwData$C)

std/sqrt(n)
qnorm(c(.06,0.94))
xbar - qnorm(.94)*std/sqrt(n)
xbar + qnorm(0.94)*std/sqrt(n)
```
Our estimate of the population mean is ~139.6. The estimated standard error of the statistic is ~0.98. Our critical value for an 88% confidence interval is given by ~1.55 and the 88% confidence interval is ~(138.1 - 141.2)


## Question 2:


#### (2.a)
```{r, q2a}
library(dplyr)

names = starwars$name
```


### (2.b)
```{r, q2b}
nchar(names[5])

nchar(names[20])

nchar(names[34])
```

### (2.c)
```{r, q2c}
num_char = numeric()
i = 0
n1 = length(names)

for(i in 1:n1){
  num_char[i] = nchar(names[i])
  i = i+1
  
}
```


### (2.d)
```{r, q2d}
num_char = sapply(names, nchar)
```

## Question 3:

### (3.a)
```{r, q3a}
boot_sample = numeric()
i = 0
for(i in 1:10000){
boot_sample[i] = median(sample(HmwData$X, 600, replace = TRUE))
i = i+1
}
```

### (3.b)
```{r, q3b}
hist(boot_sample, main = "Bootstrapped Sample Dist. for Median", prob = TRUE)

```


### (3.c)
```{r, q3c}
mean(boot_sample)

```


### (3.d)
```{r, q3d}

quantile(boot_sample, c(0.025,0.975))

```
Our confidence interval is (10,11)









