---
title: "Lab 4 Worksheet"
author: "Your name here"
date: "10/02/2021"
output: pdf_document
---

# Setup
1. Change the path in setwd to your correct path
2. Uncomment and run the install.packages("tidyverse") line. You will only have to do this one time so you can delete the line after
```{r setup}
rm(list=ls())
#setwd("~/Documents/R/STAT_123/Labs/Lab_4")
install.packages("tidyverse")
library(tidyverse)
knitr::opts_chunk$set(echo = TRUE)
```

# Data
Make sure you've placed the data files in the location you set your path to above
```{r data}
player_exposure = read.csv(file = "player_exposure.csv")
proj = read.csv(file = "nba_projections.csv")
lamelo = read.csv(file = "lamelo.csv")
```

# Clean and Format Data
You can completely ignore this part
```{r formatting}
pg = gsub(".*:","",player_exposure$PG)
sg = gsub(".*:","",player_exposure$SG)
sf = gsub(".*:","",player_exposure$SF)
pf = gsub(".*:","",player_exposure$PF)
cent = gsub(".*:","",player_exposure$C)

player_exposure = data.frame(PG = pg, SG = sg, SF = sf, PF = pf, C = cent)

freq = player_exposure %>%
  gather(Key, Name, na.rm = TRUE) %>%
  count(Name) %>% 
  arrange(desc(n))
freq = freq[2:length(freq$Name), ]

calc = function(x) {
  threes = x$X3P * 3
  twos = x$FG * 2
  ft = x$FT 
  rbd = x$TRB * 1.2
  blk = x$BLK * 2
  stl = x$STL * 2
  to = x$TOV * -1
  ass = x$AST * 1.5
  return(threes + twos + ft + rbd + blk + stl + to + ass)
}

proj[proj == "N/A"] = NA
cleaned_proj = proj %>% 
  select(Fpts, Position) %>% 
  group_by(Position) %>% 
  summarise(pts = sum(Fpts), .groups = "drop") %>% 
  drop_na()

lamelo$fpts = calc(lamelo)
```

# Question 1
Plot your pie chart in this chunk
```{r piechart}

```

# Question 2
Plot your bar plot in this chunk
```{r barplot}

```

# Question 3
Plot your time series (line graph) here
```{r timeplot}

```














