---
title: "Lab_2_Worksheet"
author: "Eric Huber"
date: "02/02/2022"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question 1:
```{r q1a}
Fdata = read.csv("FlowerData.csv")
Fdata
```


### (1.b)
Fdata is a data frame because it stores data tables that contains multiple data types. A matrix can only store one data type and Fdata stores numbers as well as characters therefore it must be a dataframe.


### (1.c)
```{r q1c}
FlowerMatrix = as.matrix(Fdata[ ,2:3])
```


### (1.d)
```{r q1d}
colnames(FlowerMatrix) <- c("Age (in days)", "Height (in cm)")
```


### (1.e)
```{r q1e}
rownames(FlowerMatrix) = c(Fdata$Individual)
```


## Question 2:

### (2.a)
```{r q2a}
mean(Fdata$Age)
```
The average age is ~37.42 days

### (2.b)
```{r q2b}
mean(Fdata$Height..cm.)
```
The average height is ~11.88 centimeters

### (2.c)
```{r q2c}
max(Fdata$Height..cm.)
max(Fdata$Age..days.)
```
The tallest flower is 19 centimeters tall and the oldest flower is 48 days old

### (2.d)
```{r q2d}
min(Fdata$Height..cm.)
min(Fdata$Age..days.)
```
The shortest flower is 4 centimeters tall and the youngest flower is 26 years old.

### (2.e)
The tallest flower from part c is yellow. The oldest flower from part c is also yellow. The shortest flower from part d is red. The youngest flower from part d is also yellow.



## Question 3:

### (3.a)
```{r q3a}
n = nrow(FlowerMatrix)
```
There are 45 rows in the matrix


### (3.b)
```{r q3b}
Samp = sample(1:nrow(FlowerMatrix), 15)


```

### (3.c)
```{r q3c}
SampleMatrix = matrix(c(FlowerMatrix[Samp, ]), nrow=15)
colnames(SampleMatrix) <- c("Age (in days)", "Height (in cm)")

```


### (3.d)
```{r q3d}
colMeans(SampleMatrix)
```
The sample average age of the flowers is ~37.07 days and the sample average height is ~11.03 cm. These results are very similar to the results found in questions 2 a/b but they are both just a bit under the actual value. That being said depending on the sample these values could fluctuate dramatically
